---
title: "DS6306_DDS_Unit2_Self_Note"
author: "Hao Wang"
date: "8/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goal: Assess if there is evidence that the relationship between city and highway mpg
# is different based on the drive of the car (4 wheel, front or rear.)
## Create a scatter plot with just the points.
```{r}
# Create a scatter
mpg %>% ggplot(aes(x=hwy,y=cty))+geom_point()
```

## Create a plot with just the smoothed line.
```{r}
mpg %>% ggplot(aes(x=hwy,y=cty))+geom_smooth()
```

## Create a plot that has a different line for each level of drive (drv).
```{r}
mpg %>% ggplot(aes(x=hwy,y=cty,linetype=drv))+geom_smooth()
```

## Create a plot that has the smoothed line and the points and designate 
## the type of drive by color... in both the line and the points.
```{r}
#Global aes() ... one aes that applies to all layers
mpg %>% ggplot(aes(x=hwy,y=cty,linetype=drv,color=drv))+geom_smooth()+geom_point()
```

## Create a plot that has the points and the smoothed line but the color
## designates the class of the car and the lines are diffentiated by the drive variable.
```{r}
#Individual aes() ... an aesthetic for each layer
ggplot(data = mpg) +
  geom_point(aes(x=hwy,y=cty,color=class))+
  geom_smooth(aes(x=hwy,y=cty,linetype=drv,color=drv))
```

```{r}
#Individual aes() ... an aesthetic for each layer
ggplot(data = mpg) +
  geom_point(aes(x=hwy,y=cty,color=class))+
  geom_smooth(aes(x=hwy,y=cty,linetype=class,color=class))+
  facet_wrap(~class)
```

